Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-09-20 manuscript/manuscript.tex
amending figure placement [ci skip]

\begin{figure}
\includegraphics[width=0.48\textwidth]{figure_1}
\caption{The HMM transition matrix $\tilde{\mathbf{P}}(\tau)$ propagates the hidden state trajectory $\tilde{s}(t)$ (orange circles) and, at each time step $t$, the emission into the observable state $s(t)$ is governed by the emission probability $\bm{\chi}\left( s(t) \middle| \tilde{s}(t) \right)$.}
\label{fig:hmm-scheme}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.48\textwidth]{figure_2}
\caption{The PyEMMA workflow: MD trajectories are processed and discretized (first row).
A Markov state model is estimated from the resulting discrete trajectories and validated (middle row).
By iterating between data processing and MSM estimation/validation,
a dynamical model is obtained that can be analyzed (last row).}
\label{fig:workflowchart}
\end{figure}

@@

>>>>

\begin{figure}
\includegraphics[width=0.48\textwidth]{figure_1}
\caption{The HMM transition matrix $\tilde{\mathbf{P}}(\tau)$ propagates the hidden state trajectory $\tilde{s}(t)$ (orange circles) and, at each time step $t$, the emission into the observable state $s(t)$ is governed by the emission probabilities $\bm{\chi}\left( s(t) \middle| \tilde{s}(t) \right)$.}
\label{fig:hmm-scheme}
\end{figure}

@@

@@

\begin{figure}[bt]
\includegraphics[width=0.48\textwidth]{figure_2}
\caption{The PyEMMA workflow: MD trajectories are processed and discretized (first row).
A Markov state model is estimated from the resulting discrete trajectories and validated (middle row).
By iterating between data processing and MSM estimation/validation,
a dynamical model is obtained that can be analyzed (last row).}
\label{fig:workflowchart}
\end{figure}
